---
title: "Task 1"
author: "Sanat Kumar Gupta"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Required Libraries
```{r}
library(VedicDateTime)
library(lubridate)
library(dplyr)
```

## Generate a Sample Time Series

```{r}
set.seed(42)
dates <- seq(ymd("2024-01-01"), ymd("2024-01-10"), by = "days")
temperatures <- runif(length(dates), min = 10, max = 35)  # Random temperatures in °C
temperature_data <- data.frame(Date = dates, Temperature = temperatures)
```

## Compute Vaara, Tithi, and Nakshatra
Define functions to compute these values for each date.

```{r}
compute_vaara <- function(year, month, day) {
  jd <- gregorian_to_jd(year, month, day)
  return(get_vaara_name(jd))
}

compute_tithi <- function(year, month, day, place) {
  jd <- gregorian_to_jd(year, month, day)
  return(get_tithi_name(jd, place))
}

compute_nakshatra <- function(year, month, day, place) {
  jd <- gregorian_to_jd(year, month, day)
  return(get_nakshatra_name(jd, place))
}
```

Set the location parameters (latitude, longitude, timezone) for calculations.

```{r}
place <- c(15.34, 75.13, +5.5)  # Example: A location in India
```


```{r}
temperature_data <- temperature_data %>%
  mutate(
    Year = year(Date),
    Month = month(Date),
    Day = day(Date),
    Vaara = mapply(compute_vaara, Year, Month, Day),
    Tithi = mapply(compute_tithi, Year, Month, Day, MoreArgs = list(place)),
    Nakshatra = mapply(compute_nakshatra, Year, Month, Day, MoreArgs = list(place))
  )
```

## Results
Display the final dataset with Vedic time attributes.

```{r}
print(temperature_data)
```

## Conclusion
This analysis demonstrates how Vedic time calculations can be integrated with natural time series data, providing insights into the alignment of temperature variations with traditional Hindu timekeeping.
